A Plasma Torus Around a Young Low-Mass Star

### 2025-03-14 paper/ms.tex
update

$R_{\rm c}$\dotfill		                  & Keplerian corotation\dotfill                                   & $1.72 \pm 0.06$  & 6 \\

@@

{\it Effective temperature, radius, mass, and spectral type}
We determined the stellar effective temperature and radius by adopting
the results from the spectral energy distribution fitting procedure
described by \cite{Bouma2024}.  To summarize, this approach used
\texttt{astroARIADNE} \cite{Vines2022} with the BT-Settl stellar
atmosphere models \cite{Allard2012}, assuming the \cite{Asplund2009}
solar abundances and the \cite{Barber2006} water line lists.  This
approach fitted for the stellar effective temperature, radius,
reddening, surface gravity, metallicity, and distance by comparing the
measured broadband magnitudes against pre-computed model grids.
Specifically, we used the broadband magnitudes from Gaia DR2, APASS,
2MASS, SDSS, and WISE $W1$ and $W2$.  This method has the most
constraining power for the star's effective temperature (2972 $\pm$
40\,K) and radius (0.42 $\pm$ 0.02\,$R_\odot$); the surface gravity,
metallicity, and reddening are typically only weakly constrained.  We
determined the star's spectral type to be M5.5Ve by visually comparing
against the photometric standards tabulated by \cite{Bochanski2007},
which agrees with the effective temperature from the SED fitting
\cite{Pecaut2013}.  Given the effective temperature, stellar radius, and
age range (35-150\,Myr) derived below, we then estimated the stellar
mass by interpolating against the PARSEC v1.2S isochrones
\cite{Chen2014}.  Specifically, we used the distance metric defined in
Equation~8 of \cite{Bouma2024} to select the model mass closest to a
given observed temperature, radius, and age.  This exercise yielded a
mass of $M_\star$=$0.20^{+0.02}_{-0.01}$ assuming an age of 35\,Myr, or
a mass of $0.25^{+0.02}_{-0.01}$ assuming an age of 150\,Myr.  
These in turn imply Keplerian corotation radii $R_{\rm
cr}/R_\star$=1.75$\pm$0.07 and $R_{\rm cr}/R_\star$=1.89$\pm$0.07,
respectively; this particular scale is relevant as it is theoretically
expected to set the inner boundary at which corotating material can
accumulate (e.g.~\cite{Townsend2005,Daley-Yates2024}).
For our final quoted $M_\star$ and $R_{\rm cr}$ values we take a
geometric mean of the extremes; we caution however that this choice is
arbitrary, and that a more precise age would be needed to circumvent
the systematic uncertainties in these parameters.

>>>>

$R_{\rm c}$\dotfill		                  & Keplerian corotation\dotfill
  & $1.82 \pm 0.10$  & 6 \\

@@

{\it Effective temperature, radius, mass, and spectral type}
We adopted the star's effective temperature and radius measured using
the spectral energy distribution fitting procedure described by
\cite{Bouma2024}.  To summarize, this approach used
\texttt{astroARIADNE} \cite{Vines2022} with the BT-Settl stellar
atmosphere models \cite{Allard2012}, assuming the \cite{Asplund2009}
solar abundances and the \cite{Barber2006} water line lists.  This
approach fitted for the stellar effective temperature, radius,
reddening, surface gravity, metallicity, and distance by comparing the
measured broadband magnitudes against pre-computed model grids.
Specifically, we used the broadband magnitudes from Gaia DR2, APASS,
2MASS, SDSS, and WISE $W1$ and $W2$.  This method has the most
constraining power for the star's effective temperature (2972 $\pm$
40\,K) and radius (0.42 $\pm$ 0.02\,$R_\odot$); the surface gravity,
metallicity, and reddening are typically only weakly constrained.  We
determined the star's spectral type to be M5.5Ve by visually comparing
against the photometric standards tabulated by \cite{Bochanski2007},
which agrees with the effective temperature from the SED fitting
\cite{Pecaut2013}.

Given the effective temperature, stellar radius, and age range
(35-150\,Myr) derived below, we then estimated the stellar mass by
interpolating against the PARSEC v1.2S isochrones \cite{Chen2014}.
Specifically, we used the distance metric defined in Equation~8 of
\cite{Bouma2024} to select the model mass closest to a given observed
temperature, radius, and age.  This exercise yielded a mass of
$M_\star$=$0.20\pm0.01$\,$M_\odot$ assuming an age of 35\,Myr, or a mass
of $0.25\pm0.01$\,$M_\odot$ assuming an age of 150\,Myr.  These masses
imply Keplerian corotation radii $R_{\rm cr}/R_\star$=1.75$\pm$0.07 and
$R_{\rm cr}/R_\star$=1.89$\pm$0.07, respectively; this size scale is
relevant because it is theoretically expected to set the inner boundary
at which corotating material might accumulate
(e.g.~\cite{Townsend2005,Daley-Yates2024}).  Our final quoted $M_\star$
and $R_{\rm cr}$ values adopt the average of these extremes and a
quadrature sum of their statistical uncertainties; we caution however
that a more precise age would be needed to resolve the systematic
uncertainties in these parameters.
